\documentclass[a4paper,11pt,parskip=half-]{scrartcl} % scrartcl for Montserrat

\input{common/common.tex}

\title{University of Warwick Computing Society Constitution}
\date{22/04/2026}

\begin{document}

\maketitle[Provisional As Of]

\vspace{1cm}
\section{Name}
\begin{enumerate}
    \item The name of the society shall be The University of Warwick Computing Society.
    \item The name of the society can also be shortened in an official capacity to ``UWCS''.
\end{enumerate}

\section{Aims and Objectives}
    \begin{enumerate}
        \item The Society shall have a written statement of aims and objectives, providing a clear understanding of the society. This shall be subject to review annually by the University of Warwick Computing Society \exec.

        \item The society aims and objectives shall be:
            \begin{enumerate}
                \item To act as the principle academic society for those studying Computer Science, related degrees, or those with interest in the field of Computer Science.

                \item To help students of all subjects become more computer literate with academic courses, resources and opportunities.

                \item To provide a welcoming and inclusive environment for like-minded people to collaborate on projects and events.

                \item To provide non-academic events to foster community within Membership.
            \end{enumerate}
    \end{enumerate}

\section{Regulations}
    \begin{enumerate}
        \item The Society, its Executives, its funds and all its activities shall be subject to the provisions of the By-Laws, Regulations and Policy of the University of Warwick Students' Union.

        \item The Society shall be subject to a disciplinary code as laid out by the Students' Union.

        \item Any alterations to the Society Constitution must be ratified by the Society Membership. Written confirmation of the ratification of the new constitution must be received prior to it taking effect.

        \item Any amendments to the constitution must be made by the end of Term 3.

        \item The renewed Constitution, with up-to-date signatures, must be sent to the Societies' Coordinator before the end of Term 3.
    \end{enumerate}

\section{Affiliation}
    \begin{enumerate}
        \item The Society is affiliated with the \href{https://www.bcs.org/membership-and-registrations/member-communities/student-chapters/}{British Computing Society, The Chartered Institute for IT}.
    \end{enumerate}

\section{Memberships}
    \begin{enumerate}
        \item Memberships of the Society shall be open to all full, associate, and honorary members of the Students' Union upon payment of the required Societies Federation subscription.

        \item Memberships of the Society are to be renewed on the 1st September of every year.
            \begin{enumerate}
                \item Associate membership will be decided by a \hyr{exec-quorum}{quorate} vote within the Society Executive.

                \item New Associate membership will only be granted such that standard members always represent the absolute majority of the full membership of the Society.
            \end{enumerate}

        \item The Society must have a minimum of 30 standard members by the sixth week of each academic term, in order to remain affiliated with the Students' Union.
    \end{enumerate}

\section{Cost of Membership}
    \begin{enumerate}
        \item Standard Membership of the Society shall be free, or £0.00.

        \item Associate Membership of the Society shall be £3.00.
    \end{enumerate}

\section{Eligibility to Vote \& Nominate}
    \begin{enumerate}
        \item All standard members of the society shall be entitled to hold office of an Executive position and vote in elections or General Meetings.

        \item For avoidance of doubt, the following shall not be entitled to hold the office of an Executive position or vote in the society:
            \begin{enumerate}
                \item An Associate or Honorary member of the Students' Union.

                \item Any standard member of the society who has not joined the society no less than fourteen days before voting begins.
            \end{enumerate}

        \item For avoidance of doubt, the following roles shall be protected by the following limitations:
            \begin{enumerate}
                    \item\label{frep-restriction} Freshers' Representatives positions are recognised as protected positions, restricted to only first year undergraduate members. Voting for Freshers' Representatives positions shall be exempt from \hyr{general-quorum}{quorum}.

                    \item\label{gender-inclusivity-restriction} \hyr{gender}{Gender Inclusivity Officer} and Gender Inclusivity \hyr{frep}{Freshers' Representative} are recognised as protected positions, restricted to only members who do not self-identify as cisgender men. Voting for \hyr{gender}{Gender Inclusivity Officer} and Gender Inclusivity \hyr{frep}{Freshers' Representative} positions shall be exempt from \hyr{general-quorum}{quorum}.

                    \item\label{ethnic-minority-restriction} \hyr{em}{Ethnic Minorities Rep} positions are recognised as protected positions, restricted to only self-identified Ethnic Minority members. Voting for \hyr{em}{Ethnic Minorities Rep} positions shall be exempt from \hyr{general-quorum}{quorum}.
            \end{enumerate}

        \item Defined restrictions in~\ref{frep-restriction} \&~\ref{gender-inclusivity-restriction} \&~\ref{ethnic-minority-restriction} additionally apply to members' eligibility to:
            \begin{enumerate}
                \item Nominate for the positions
                \item Hold the positions
                \item Vote on elections for the positions
            \end{enumerate}
    \end{enumerate}

\section{Election Procedures}
    \begin{enumerate}
        \item Annual Elections, including the election of the \exec, must occur between week five and week nine (inclusive) of Term 2 of the University of Warwick academic year.
            \begin{enumerate}
                \item Elections shall be held at a \hyr{general-quorum}{quorate} general meeting. The manner and procedures of this election shall be determined by the \exec provided they do not contradict the constitution or SU regulations and by-laws.

                \item The Student Union shall be the Returning Officer for all Society elections.The \exec shall appoint a Deputy Returning Officer through a \hyr{exec-quorum}{quorate} vote, provided there is no actual or perceived conflicts of interest.
            \end{enumerate}

        \item Votes for elected positions will be counted using a Single Transferable Vote electoral system and re-open nominations (R.O.N) shall be present on all ballot, with First Past The Post/simple majority used in votes on motions.

        \item All elections shall be conducted with a secret ballot.

        \item\label{general-quorum} Quorum for General Meetings or By-Elections shall be equivalent to 7\% of Society Membership.

        \item\label{exec-quorum} Quorum for \exec votes shall be equivalent to 50\% + 1 of the \exec. Such votes should have a minimum time period of 72 hours, with exceptions for urgent time-sensitive matters.
    \end{enumerate}

\section{Executive Committee}\label{sec:exec}
    \begin{enumerate}
        \item The Society's Executive Committee (which may also be referred to as the ``Motherboard'') shall be made up of at least the President, a Welfare Officer, and a Treasurer.
        
        \item The Executive Committee shall be responsible for the day to day running of the society and may decide upon any matter that has not yet been decided upon by the General Meeting. The Executive Committee shall further be responsible for:
            \begin{enumerate}
                \item Organising the activities of the Society in such a way as to include the greatest possible number of Society members.

                \item Managing the expenditure of the Society's funds in a responsible fashion and in line with the aims, objectives and planned activities of the Society whilst adhering to the SU's financial regulations.

                \item Formulating and submitting an annual bid for funds from the Societies Executive prior to any specified deadline which shall include a statement of activities and objectives for the coming year and detailed justification of the figures contained in the bid.

                \item Formulating and submitting any additional bids for funds from the Societies Executive or groups within the Students' Union.

                \item Assisting any review of the Society's activities and use of funds carried out by a standing committee or group of the Students' Union that has granted funds to the Society.

                \item Upholding the Constitution of the Society and ensuring that its aims and objectives reflect the Society activities.

                \item Ensuring that all society activity abides by the governance Warwick Student's Union.

                \item Executive Committee members must attend assigned training to ensure they are equipped to organise the Society.
            \end{enumerate}
        
        \item\label{seats-rule} Each position shall be filled:
            \begin{enumerate}
                \item By one (1) seat:
                    \begin{enumerate}
                        \item \hyr{pres}{President}
                        \item \hyr{treasurer}{Treasurer}
                        \item \hyr{sec}{Secretary}
                        \item \hyr{sports}{Sports Officer}
                        \item \hyr{ball}{Ball Officer}
                        \item \hyr{vp}{Vice President}
                        \item \hyr{em}{Ethnic Minorities Rep}
                        \item \hyr{pg}{Postgraduate Rep}
                    \end{enumerate}
                \item By up to two (2) seats:
                    \begin{enumerate}
                        \item \hyr{welfare}{Welfare Officer}
                        \item \hyr{social}{Social Secretary}
                        \item \hyr{gender}{Gender Inclusivity Officer}
                        \item \hyr{publicity}{Publicity Officer}
                    \end{enumerate}
                \item By up to three (3) seats:
                    \begin{enumerate}
                        \item \hyr{academic}{Academic Coordinator}
                        \item \hyr{gaming}{Gaming Coordinator}
                    \end{enumerate}
                \item By up to four (4) seats:
                    \begin{enumerate}
                        \item \hyr{tech}{Technical Officer}
                    \end{enumerate}
                
                \item Additional positions should be filled in accordance with~\ref{vacant-rule}.
            \end{enumerate}
        
        \item\label{vacant-rule} Should a position not reach its quota as defined in~\ref{seats-rule}, if its elections are \hyr{general-quorum}{not quorate}, or if Re-Open Nominations (R.O.N) wins the election, the incoming exec should treat the empty position as a vacant slot.
        
        \item This selection cannot pass a vote to Re-Open Nominations (R.O.N).
        
        \itemb{Additional Seats}
            \begin{enumerate}
                \item\label{extra-seats-rule} In the event of additional demand or other extraordinary circumstance, a \hyr{exec-quorum}{quorate} vote from the Executive Committee can add a maximum of 2 seats to any individual role.
                    \begin{enumerate}
                        \item The positions of \hyr{pres}{President}, \hyr{vp}{Vice President} and \hyr{frep}{Freshers' Representative} shall be exempt from~\ref{extra-seats-rule}.
                    \end{enumerate}

                \item Additional seats will be filled by an Extraordinary General Meeting (EGM) or By-Election.

                \item Multiple members are not permitted to run together for one seat.

                \item Additional seats will not be cumulative, and will be reset with each subsequent Annual General Meeting (AGM).
            \end{enumerate}
        
        \itemb{Core Officers}
            \begin{enumerate}[series=core]
                \item The Core Officer Duties shall include:
                \begin{enumerate}
                    \item To attend the Society's Annual General Meeting.

                    \item To attend Societies Council and complete mandatory training sessions/courses.
                \end{enumerate}
            \end{enumerate}
    \end{enumerate}

    \doublelistbreak{The core officers shall be:}

    \begin{enumerate}[resume]
        \item[]{}

        \begin{enumerate}[resume=core]
            \item[]{}
            
            \begin{role}{President / Lord/Lady/Liege/etc Chancellor of the Computers}{pres}
                \item The President will organise and oversee the running of The Society in line with goals outlined with this Constitution.

                \item The President will seek to guide the direction of the Society as a whole - with considerations made to the ``Bigger Picture'' and future of the Society.

                \item The President will work alongside the Executive Committee to produce written documentation to aid future Executive Committee members where appropriate.

                \item The President will chair committee meetings.

                \item The President will produce an annual report.

                \item The President will work with the \hyr{welfare}{Welfare Officer(s)} to ensure member wellbeing both at society events and within society run channels. With such issues, the President is bound by confidentiality.

                \item The President will aim to promote strong Executive Committee cohesion, individual agency and where appropriate, accountability. 
            \end{role}

            \begin{role}{Treasurer}{treasurer}
                \item The Treasurer is responsible for the finances of the Society.

                \item The Treasurer will maintain an up-to-date record of their group account in addition to the record kept by the SU finance office.

                \item All funds will be held and processed through the groups Students' Union bank account. No money will be held in personal bank accounts.

                \item The Treasurer will submit grant funding applications.

                \item The Treasurer will build and maintain relationships with organisations that sponsor the Society.

                \item The Treasurer will maintain an up-to-date annual budget for all relevant areas of the Society, which must include, but is not limited to:
                    \begin{enumerate}
                        \item \hyr{welfare}{Welfare}
                        \item \hyr{gender}{Gender Inclusivity}
                        \item \hyr{gaming}{Gaming}
                        \item \hyr{social}{Social}
                        \item \hyr{academic}{Academic}
                        \item \hyr{ball}{Ball}
                        \item \hyr{tech}{Tech}
                        \item \hyr{sports}{Sports}.
                    \end{enumerate}
            \end{role}

            \begin{role}{Welfare Officer}{welfare}
                \item The Welfare Officer will work confidentially with both society members and exec to prioritise their wellbeing and safety, be available as the first point of contact, and where appropriate, signpost to external services such as Wellbeing Services and Report \& Support.

                \item The Welfare Officer is not professionally trained, and will not act in a professional capacity, including, but not limited to, a therapist.

                \item The Welfare Officer will, as appropriate, inform event organiser(s), the \hyr{pres}{President}, or sources of authority within the university/SU, where issues require greater intervention (for example, where members' safety is at direct risk), or where there are issues such as a conflict of interest. The Welfare Officer will also not seek to override official processes, such as those by Report \& Support.

                \item The Welfare Officer will engage with learning materials such as those provided by (but not strictly limited to) the Active Bystander course and Report \& Support.

                \item For non-sober events, the Welfare Officer will liaise with the \hyr{social}{Social Secretaries} to ensure the presence of a minimum of two (2) ``sober exec''. At least one (1) Welfare Officer is expected to be in attendance as ``sober exec''.
            \end{role}
        \end{enumerate}

        \itemb{Additional Officers}
            \begin{enumerate}
                \begin{role}{Academic Coordinator}{academic}
                    \item The Academic Coordinator will organise the academic events, such as external guest speakers, presentations on areas relating to Computer Science and workshops.
                    \item The Academic Coordinator will act as the point of contact for organisation of events with external speakers, university departments, or other students.
                \end{role}

                \begin{role}{Ball Officer}{ball}
                    \item The Ball Officer will be responsible for coordinating the Computing Ball.
                \end{role}

                \begin{role}{Freshers' Representative}{frep}
                    \item The Freshers' Representative will facilitate first year undergraduate engagement and events within the society.

                    \item The Freshers' Representative will act as a point of contact between the Executive Committee and for first year undergraduate students.

                    \item Up to one (1) Freshers' Representative will be elected for each of the following categories:
                        \begin{enumerate}
                            \item \hyr{academic}{Academic}
                            \item \hyr{social}{Social}
                            \item \hyr{gender}{Gender Inclusivity}
                            \item \hyr{gaming}{Gaming}
                            \item \hyr{tech}{Technical}.
                        \end{enumerate}

                    \item The Freshers' Representative will hold their position until the reset of Society Memberships at the start of September, such that they act as a continuing point of contact in the interim between the AGM and the next Fresher Representative elections in Term 1.

                    \item The Freshers' Representative for each category will assist with and be supported by their relevant executive members in the planning and running of events they perceive as relevant to their year, along with the general activities of the society.

                    \item This office will be elected in a Extraordinary General Meeting (EGM) or by-election run between weeks one to five of Term 1.
                \end{role}

                \begin{role}{Gaming Coordinator}{gaming}
                    \item The Gaming Coordinator will organise all gaming-related events.

                    \item The Gaming Coordinator will organise weekly gaming events, termed ``Friday Night Gaming''.

                    \item The Gaming Coordinator will, exceptions withstanding, organise other gaming related events, such as LANs.
                \end{role}

                \begin{role}{Gender Inclusivity Officer}{gender}
                    \item The Gender Inclusivity Officer will help create and maintain a welcoming atmosphere for marginalised genders in the society.

                    \item The Gender Inclusivity Officer will act as a point of contact for organising events aimed to promote initiatives beneficial towards under-represented gender demographics in Computer Science and liaise with the department in this capacity.
                \end{role}

                \begin{role}{Publicity Officer}{publicity}
                    \item The Publicity Officer will review and post announcements to secondary social media platforms.

                    \item The Publicity Officer is responsible for creating graphics for society announcements and operation.
                \end{role}
                
                \begin{role}{Secretary}{sec}
                    \item The Secretary will act as the point of contact for general enquiries with the society.

                    \item The Secretary will take minutes of every Society Executive Committee meeting and publish them to all members on the Society website within one week of the meeting taking place. This responsibility also includes the minuting of Society General Meetings, such as the Annual General Meeting.

                    \item The Secretary will write weekly newsletters during each academic term, to provide details of the upcoming week's events, as well as any other relevant notices. These newsletters should be circulated to all members by no later than Monday of the relevant week, with the exception of extraordinary circumstances.

                    \item The Secretary will organise all clothing and merchandise orders for members of the society.
                \end{role}

                \begin{role}{Social Secretary}{social}
                    \item The Social Secretary will organise the social events run by the society each term.

                    \item The Social Secretary will act as the convenor with other society Executive Committees for the purpose of organising a collaborative social.

                    \item The Social Secretary will work with the \hyr{welfare}{Welfare Officer(s)} to ensure the presence of ``sober exec'' at non-sober events.

                    \item The Social Secretary will create a welcoming, inclusive and accessible environment by ensuring the safety and welfare of all members at any and all Society-run socials.
                \end{role}

                \begin{role}{Sports Officer}{sports}
                    \item The Sports Officer will organise sporting events for the society.

                    \item The Sports Officer will involve the society in campus leagues.
                \end{role}

                \begin{role}{Technical Officer}{tech}
                    \item The Technical Officer will oversee the running of the digital and physical services offered by the Society.

                    \item The Technical Officer will appropriately document all projects and services, such that they are accessible to all members, and maintainable for future Technical Officers.

                    \item The Technical Officer will disclose any planned maintenance periods for society services at least 7 days before maintenance is to begin except in circumstances where information on timelines, such as maintenance in the Department of Computer Science, or other areas of the University, are not concretely established at the 7 day cut-off.

                    \item The Technical Officer will be the point of contact for recording of event sessions.
                \end{role}

                \begin{role}{Vice President/Vice Chancellor of the Computers}{vp}
                    \item The Vice President will assist the \hyr{pres}{President} with their duties as required, as well as assisting other members of the Executive Committee when necessary.

                    \item The Vice President will execute the duties of the \hyr{pres}{President} in the event of the extended absence or resignation of the \hyr{pres}{President}, in the capacity of acting President, for a maximum of 10 weeks, until the next Extraordinary or Annual General Meeting.

                    \item In the event of the resignation and/or extended absence of both the \hyr{pres}{President} and Vice President, the Executive shall elect by a supermajority \hyr{exec-quorum}{quorate} vote, an existing member of exec to serve as acting \hyr{pres}{President}, for a period no longer than 10 weeks, an election is held for their replacement.
                \end{role}

                \begin{role}{Ethnic Minorities Representative}{em}
                    \item The Ethnic Minorities Representative will endeavour to facilitate and drive engagement and events for ethnic minorities within the society.

                    \item The Ethnic Minorities Representative will act as a first point of contact between ethnic minorities and the Executive Committee.

                    \item The Ethnic Minorities Representative will help and create a welcoming atmosphere for ethnic minorities within the society by hosting varied events to create community with support from the Executive Committee.

                    \item The Ethnic Minorities Representative will act as a point of contact for organising events aimed to promote initiatives beneficial towards under-represented demographics in Computer Science and liaise with the department in this capacity.
                \end{role}

                \begin{role}{Postgraduate Representative}{pg}
                    \item The Postgraduate Representative will endeavour to facilitate and drive Postgraduate engagement and events within the society.

                    \item The Postgraduate Representative will act as a first point of contact between Postgraduate students and the Executive Committee.

                    \item The Postgraduate Representative will help and create a welcoming atmosphere for Postgraduate members of the society by hosting varied events to create community with support from the Executive Committee.

                    \item This office will be elected in a by-election or EGM run between weeks one to five of Term 1.

                    \item The Postgraduate Representative will hold their position until the reset of Society Memberships at the start of September, such that they act as a continuing point of contact in the interim between the AGM and the next Postgraduate Representative elections in Term 1.
                \end{role}

                \begin{role}{Outreach Officer}{outreach}
                    \item The Outreach Officer will be responsible for, in coordination with relevant exec, building and maintaining relationships with external organisations and stakeholders - such as sponsors, guest speakers, university departments etc.

                    \item The Outreach Officer will be responsible for ensuring communication with external stakeholders is done in a timely and professional manner.
                \end{role}
            \end{enumerate}
    \end{enumerate}

\section{Tech Team}
    \begin{enumerate}
        \item ``Sysadmin'' is a recognised role that:
            \begin{enumerate}
                \item Is \textbf{not} part of the \exec.
                \item Shows official capacity in managing society technical matters.
                \item Is automatically granted to serving \hyr{tech}{Tech Officers}.
                \item Shall be granted, subject to a vote by serving \hyr{tech}{Tech Officers}, to requesting members.
                \item Shall be recognised by the Sysadmin role on the \href{https://discord.uwcs.uk}{Society's Discord server}.
            \end{enumerate}
        \item The Tech Team shall comprise of Sysadmins.
    \end{enumerate}

\section{Meetings}
    \begin{enumerate}
        \item The Executive must meet at least two times per term to ensure the Society is operated to a high standard. All Executive will have attending General Executive Meetings, and Executive Meetings specific to the positions held, as an additional role responsibility, and repeated failure to attend will be considered not meeting said responsibilities.

        \item The Society Executive shall call at least one General Meeting per year for the purposes of discussing plans and activities for the coming year. This must be held by end of Week 9, Term 2. At least the Annual General Meeting, and Fresher Representative EGM, will be used to hold Society Executive elections.

        \item The Society Executive shall give at least 14 days' notice of any General Meeting to all members via Society email and such notice shall include details of any elections to be held.

        \item The Executive shall call further meetings either a majority quorate vote of the Executive, or at the request of 10\% of the membership or the request of the Societies Officer.

        \item All motions proposed for a General Meeting should have a copy made of and stored in a \href{https://github.com/uwcs/democracy}{repository} for at least 5 years from the General Meeting. This should be stored alongside:
            \begin{enumerate}
                \item Its date of proposal.
                \item The outcome of its vote.
            \end{enumerate}
            All motions and additional information in the above repository should be made accessible to all members of the society.
    \end{enumerate}

\section{Code of Conduct}\label{sec:coc}
    \begin{enumerate}
        \item\label{bound-coc} Members of the Society Executive shall be bound by the below regulations, and should be considered additional role responsibilities for all Executive positions.

        \item Executive members should be reachable in a timely manner by other members of the executive. If a member of the executive wishes to step down or take an extended leave of absence, they should communicate as such to the \hyr{pres}{President} and the rest of the \exec at large.
            \begin{enumerate}
                \item Communication within the Society Executive is done primarily via the \href{https://discord.uwcs.uk}{Society's Discord server}.
                \item For a general member of the executive, an extended leave of absence is to be defined as any absence longer than 2 weeks.
            \end{enumerate}

        \item Executive members have a fiduciary responsibility to the society. There should be no tolerance for abuse of Society funds or property. Executive members should take all necessary steps - individually and collectively - to ensure the security of Society property, and the financial wellbeing of the Society. Therefore, it will be considered a breach of this regulation to use Society property for non-Society activities, without the permission of the relevant executive members, and informing the Executive at large.

        \item Executive members have a responsibility for the general welfare of members at Society events. Executive members should not, under any circumstances, engage in harassment or abusive, threatening, or coercive behaviour of any kind towards other members; executive members should also act as ``active bystanders'', and take all steps necessary to prevent and respond to such behaviours in others, pursuant to creating and maintaining a safe and welcoming environment for all members.

        \item The Society shall not be affiliated with any particular political party or set of parties. The Society Executive should not engage the Society in political activity which may alienate or otherwise negatively impact the members of the Society based on their political affiliations.

        \item The Society Executive shall not make use of Social Media - either personal or of the Society - in such a way that brings the Society into disrepute, or in any other way that contravenes~\ref{bound-coc}.

        \item The Society Executive must not engage in actions or language that are discriminatory on the basis of race, religion, nationality, age, sex, sexual orientation, gender identity, or disability.
        
        \item The regulations in \eref{sec:coc} extend to both in-person and online spaces, wherever applicable.
    \end{enumerate}

\end{document}
